Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 cross_compilation.tex
worked on cross compiling

WRITE INTRO OF WHY WE WANT TO CROSS COMPILE. E.G. 1) WE DO NOT HAVE MONITORS
CONNECTED TO THE RASPIS, 2) A PC IS SIGNIFICANTLY FASTER AND FAR BETTER EQUIPPED (RAM, CPU, HARDDRIVE), 3) MORE CONVINIENT TO DO EVERYTHING IN ONE PC AND DISTRIBUTE IT TO THE RASPIS AFTERWARDS. MORE?

@@

Besides the previous description (\textbf{Include compiling Kodo from the
RasPi from the scratch}), the testbed administrator can compile Kodo in its
personal workstation and transfer the generated binaries directly to
a path in the \ac{Raspi}. To achieve this, we get a toolchain that
contains the binaries for the \texttt{raspberry-gxx49-arm-g++} compiler
for the \ac{Raspi}. Therefore, we strongly recommend any testbed
administrator to do the following procedure. In what follows, we provide
the instructions considering that the NFS server uses the \texttt{\$HOME}
directory as the working directory. However, the administrator may choose
some other working directory of its preference if desired.

@@

Create a directory to hold our code:
\begin{lstlisting}[]
$ CODEDIR="${HOME}/code"
$ mkdir -p ${CODEDIR}
$ cd ${CODEDIR}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Create a \texttt{hello\_world.cpp} using your favorite text editor:

@@

Lets copy the executable file to a \ac{Raspi} and test it. We will use \ac{SCP}
to copy the executable to one of the \ac{Raspi}s.

Default username is "pi" and password is "raspberry"

@@

Now, simply execute the \texttt{hello\_world}:

@@

WRITE SOME SMALL INTRO AND MENTION HOW TO REQUEST A KODO LICENSE

>>>>

Modern \ac{PC}s are significantly better equipped than the \ac{Raspi}s that in
contrasts to \ac{PC}s target a far more affortable and smaller module size. This
means that it may be preferred or even mandatory to perform some computational
expensive tasks in a \ac{PC} rather than in \ac{Raspi}s.
Example of tasks that are quite computational expensive is to compile software
packages and large libraries.
Another reason to use a \ac{PC} may be the hardware limitations of \ac{Raspi}s
in terms of e.g. memory and disk space. Some software packages might simply be
too memory demanding to be compiled in a \ac{Raspi}.
Thus, this section will present how to setup a toolchain in a \ac{PC} that can
be used to cross compile C++ code to the ARM architecture that the \ac{Raspi}s.
The toolchain is mandatory on most consumer \ac{PC}s due to the different
processor architecture.

Furthermore, we will cover how to cross compile a simple C++ example and
Kodo-cpp as well as how the binaries can be copied from a \ac{PC} to a
\ac{Raspi} and executed.
There exists bindings to Kodo in various programming language. We will present
how to also run a Kodo-python application in a \ac{Raspi}.

%WRITE INTRO OF WHY WE WANT TO CROSS COMPILE. E.G. 1) WE DO NOT HAVE MONITORS
%CONNECTED TO THE RASPIS, 2) A PC IS SIGNIFICANTLY FASTER AND FAR BETTER EQUIPPED (RAM, CPU, HARDDRIVE), 3) MORE CONVINIENT TO DO EVERYTHING IN ONE PC AND DISTRIBUTE IT TO THE RASPIS AFTERWARDS. MORE?

@@

%Besides the previous description (\textbf{Include compiling Kodo from the
%RasPi from the scratch}), the testbed administrator can compile Kodo in its
%personal workstation and transfer the generated binaries directly to
%a path in the \ac{Raspi}. To achieve this, we get a toolchain that
%contains the binaries for the \texttt{raspberry-gxx49-arm-g++} compiler
%for the \ac{Raspi}. Therefore, we strongly recommend any testbed
%administrator to do the following procedure. In what follows, we provide
%the instructions considering that the NFS server uses the \texttt{\$HOME}
%directory as the working directory. However, the administrator may choose
%some other working directory of its preference if desired.

@@

The following example will provide a very basic example of 1) how to cross compile
a \texttt{hello\_world} c++ example to the \ac{Raspi}'s ARM architecture
and 2) how to copy and execute the binary in a \ac{Raspi} using \ac{SCP} and \ac{SSH}.

Lets create a directory to hold our code:
\begin{lstlisting}[]
$ CODEDIR="${HOME}/code"
$ mkdir -p ${CODEDIR}
$ cd ${CODEDIR}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Create the file \texttt{hello\_world.cpp} with the following content using your
favorite text editor:

@@

This should produce a binary \texttt{hello\_world}. Copy it to a \ac{Raspi}
and test it. We will use \ac{SCP} to copy the binary file to one of the \ac{Raspi}s.

The default username for our Raspbian lite distribution is "pi" and password is "raspberry"

@@

Now, simply execute the \texttt{hello\_world} to confirm that cross compiling
\texttt{hello\_world} worked properly:

@@

Kodo is a C++11 library for \ac{NC}. There exists a number of bindings for
Kodo to other popular programming languages. This procedure will go through
how to setup Kodo-cpp to cross compile to \ac{Raspi}. Kodo-cpp provides a
simple interface to the underlying C++11 code that exists in the libraries
Kodo-core and Kodo-rlnc.

In order to use Kodo, it is required to obtain a research- and
education-friendly license.
A license can be obtained from \url{http://steinwurf.com/license.html}. It is
free for research and educational purposes.
